---
title: "Some amazing data visualizations"
subtitle: "Seriously, can you believe how amazing?"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable
---

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(reactable)
library(harrypotter)
theme_set(theme_minimal(base_size = 25) +
            theme(plot.title.position = "plot",
                  legend.position = "bottom"))
```


Description of data {.sidebar}
=====================

This is a dashboard built with datasets that ship with [R](https://cran.r-project.org), including [**Fisher's iris dataset**](https://en.wikipedia.org/wiki/Iris_flower_data_set) and the [Moter Trends Cars dataset](http://www.sthda.com/english/wiki/r-built-in-data-sets). 


# iris {data-icon="fa-seedling"}
Here's the iris dataset I was telling you about in the sidebart.

Column {.tabset data-width=650}
------------------------

### Scatterplot 

This scatterplot took a lot of work (most of it picking which color the points would be).

```{r, fig.width = 12}
ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species), size = 2) +
  geom_smooth(color = "magenta",
              fill = "cornflowerblue") +
  scale_colour_hp_d(option = "ravenclaw")
```

> Awesome caption about a boring plot

### Table

The table below is interactive. Feel free to click around!

```{r tbl1}
reactable(iris)
```

> This is the table

Column {data-width=350}
-----------------------------------------------------------------------

### Sepal Length by Species

```{r, iris-bar, fig.height = 10}
iris %>% 
  group_by(Species) %>% 
  summarize(mean_sepal_length = mean(Sepal.Length)) %>% 
  ungroup() %>% 
  mutate(Species = fct_reorder(Species, 
                               mean_sepal_length)) %>% 
  ggplot(aes(Species, mean_sepal_length)) +
  geom_col(fill = "cornflowerblue") +
  coord_flip() +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "",
       y = "Mean Sepal Length")
```


# mtcars {data-icon="fa-car"}

Column {data-width=500}
-----------------------------------------------------------------------

### Scatterplot
```{r scatter-mtcars, fig.width = 7}
ggplot(mtcars, aes(disp, mpg)) +
  geom_point(aes(color = factor(carb))) +
  geom_smooth() +
  labs(x = "Engine Displacement",
       y = "Miles Per Gallon") +
  scale_colour_hp_d(name = "Carb", option = "slytherin")
```

### Table

```{r mtcars-tbl}
reactable(mtcars)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar chart

```{r barchart-mtcars, fig.height = 9}
p <- mtcars %>% 
  rownames_to_column("car") %>% 
  group_by(cyl) %>% 
  summarize(mean_mpg = mean(mpg)) %>% 
  ggplot(aes(factor(cyl), mean_mpg)) +
  geom_col(fill = "magenta") +
  coord_flip() +
  labs(x = "Cylinders",
       y = "Mean miles per gallon")

plotly::ggplotly(p)
```

# More stuff {data-icon="fa-500px"}